Completing Programs with Relational Types

### 2023-11-27 paper/relationaltypes.tex
update tests, add piping of exceptions into guidance
add parsing for if-then-else and funnel pipeline

Using attribute rules during parsing adds many complications that would not be present for an
analysis over an AST. 
The analysis must be separated into rules for \textit{inheriting attributes} and rules for \textit{synthesizing attributes}.
Additionally, due to the left-recursion problem in top-down parsing, 
the parser consolidates information in a right-associative manner.
Thus, one difference of an analysis over a top-down parsing stack as opposed to recursion over an AST is 
the re-associating of program information from right to the left on the fly. 
Consider a chain of record selections:  
\[ 
x.uno.dos.tres 
\]

@@

>>>>

@@

Using attribute rules during parsing adds many complications that would not be present for an
analysis over an AST. 
The analysis must be separated into rules for \textit{inheriting attributes} and rules for \textit{synthesizing attributes}.
Additionally, due to the left-recursion problem in top-down parsing, 
the parser consolidates information in a right-associative manner.
Thus, one difference of an analysis over a top-down parsing stack as opposed to recursion over an AST is 
the re-associating of program information from right to the left on the fly. 
Consider a chain of record projections:  
\[ 
x.uno.dos.tres 
\]

Propagating types downward over a top-down parse-tree results in a varying interpretations of the downwardly propagated type used for local guidance.
For syntax that represents complete expressions, e.g. \[ :uno @ \], the inherited type represents the expected type for that expression.
However, for syntax that cannot represent a complete expression, the inherited type must represent something else. 
For instance, in the parse tree for a chain of projections, a syntactic subtree of projections, such as \[ .dos.tres \] does not constitute a complete expression.   
There is no type for this syntax. Thus, the inherited type represents the type that \[ .dos \] is expected to project from (or cut into), 
e.g. the descriptive type of \[ x.uno \].
